RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
note formatting error: the citations run off the page of the PDF
maybe not go into XPath applied to RDF?

Common metadata can be accessed with a few dedicated functions:

@@

Query the rdf using XPath expressions:

>>>>

<!-- the citations run off the page -->
Common metadata can be accessed with a few dedicated functions:

@@

<!-- I think it is unwise to go here: RDF is not structured data -->
Query the rdf using XPath expressions:
